### 2019-07-19 manuscript.tex
Update manuscript.tex

Multiple theoretical frameworks were \jdcmt{what does this mean; called to be incorporated to grasp a full explanation} of the persistence and decline of FGC due to the heterogeneity of the population \cite{EffeVogt15, ModrLiu13} \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} applied on fgc \icte{CislHeis18, EffeVogt15, Harf06, PashPonn16, ShelHern06,}}  In this study, we consider multiple social determinants of FGC practice both at a individual and a community level to analyze how community of FGC expectation and beliefs associates with individual attitudes on the practice.  In addition to \jdcmt{hard to figure out what this means in this context, do you just mean attitudes about FGC? social norms of FGC,} we also incorporated information about women’s gender values and their \jdcmt{Can you explain this? social environment.}

@@

\jdcmt{Do we really call our three models: daughter; persistence; and daughter persistence? It does not seem conducive to reader understanding.}

@@

\subsubsection{Data and Samples}\label{data-and-samples}

\jd{What is added by ``and samples'' here?}

We conducted secondary analysis of women aged 15-49 in the Demographic and Health Surveys (DHS).  We selected countries with: high FGC prevalence \cite{UNIC16}, and FGC benefit and gender awareness modules available from DHS. We found four countries, and used the most recent complete data set from each: Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.  We did not analyze the newest dataset \jdcmt{What data set did we not analyze? Can we just say we analyzed the newest available (see edits above)? Also: these are pretty old.} due to the lack of FGC benefits modules before this study finished for publication \cf{checked in 1/09/19}.

@@

\subsubsection{Measurements and Concepts}\label{measurements-and-concepts}

@@

Our main response variables were woman's \jdcmt{I don't think this work adds anything; behavioural} reported intention to cut their daughters in the daughter model and the mixed (daughter-persistence) model, and woman's attitude on whether FGC should be continued in the persistence model.  \jdcmt{You are describing just some predictors; The predictors selected} \jdcmt{I don't know what is being conveyed here, can we lose it? based on literature (e.g., aforementioned above)} were woman's FGC status and beliefs about FGC benefits (see supp for the benefit questionnaire).  The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm} to identify the strength of benefits associating with fgc practice. We also included gender awareness (see — for questions of gender awareness proxy) in our models to test if women’s self-awareness would moderate \cf{wording} their intention of FGC practice \cfonly{cites of feminist theory on fgc}. Other socio-demographic variables included were:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media use and residence (urban vs. rural) in addition to country.  Media use and gender awareness were scored.  The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).

>>>>

In this study, we consider multiple social determinants of FGC practice both at an individual and a community level to analyze how FGC norm at a community level associates with that at an individual level in predicting the persistence of FGC practice \cfcmt{in the presumption that attitudes is a good proxy of social norm \cite{}}.  \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} applied on fgc \icte{CislHeis18, EffeVogt15, Harf06, ModrLiu13 , PashPonn16, ShelHern06,}}

@@

\jdcmt{Do we really call our three models: daughter; persistence; and daughter persistence? It does not seem conducive to reader understanding.} \cfcmt{That was what we agreed.  We don’t really like the names but couldn’t come up with a better one. How about daughter, fgc continuity, and structural mixed model?}

@@

\subsubsection{Data}\label{data}

We conducted secondary analysis of women aged 15-49 in the Demographic and Health Surveys (DHS) with FGC benefit and gender awareness modules in countries with high FGC prevalence \cite{UNIC16}. We found four countries, and used the most recent complete data set from each: Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.  \jdcmt{these are pretty old.} \cfcmt{checked in 1/09/19.  Yes.  Those datasets are pretty old but were the most recent ones with fgc benefits modules.}.

@@

\subsubsection{Measurements}\label{measurements}

@@

Our main response variables were woman's reported intention to cut their daughters in the daughter model and the mixed (daughter-persistence) model, and woman's attitude on whether FGC should be continued in the persistence model.  The main predictors were woman's FGC status and beliefs of FGC benefits (see supp for the benefit questionnaire).  The beliefs of FGC benefits were quantified using average score \cfcmt{pls confirm} to identify the strength of benefits associating with fgc practice. We also included gender awareness (see — for questions of gender awareness proxy) in our models to test if women’s self-awareness would moderate \cf{wording} their intention of FGC practice \cfonly{cites of feminist theory on fgc}. Other socio-demographic variables included were:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media use and residence (urban vs. rural) in addition to country.  Media use and gender awareness were scored.  The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).
